Declarative Deployment Reconfiguration of Pulverised Collective Adaptive Systems at Runtime \thanks{Identify applicable funding agency here. If none, delete this.}

### 2023-05-16 paper-2023-acsos-pulverization.tex
pass on 3.A

The infrastructure \ac{dsl} captures the concepts of
\emph{logical device}, \emph{component}, \emph{capability}, and \emph{requirement}.
%

The DSL enables the definition of the type of devices that take part in the system,
and for each device can be specified which components constitute it and where those component must run on (e.g. which host must execute the component).
%
The execution of a component is constrained to hosts with predetermined characteristics:
the framework models the constraint with the \texttt{Capability} concept,
namely the property that a host must to ``implement'' to run the component.
%
Different capabilities can be specified for each component to provide a more flexible and scalable deployment of the system.

The~\Cref{lst:system-configuration} provides an example of the usage of the domain-specific language where is defined a system composed of two kind of devices.
%
The DSL returns the system's configuration that will be used by the runtime.

One key-point of the domain-specific language can be observed in the definition of the \texttt{device-2} device:
the \emph{Behaviour} component can be deployed on hosts that implement the \texttt{HighCPU} and \texttt{EmbeddedDevice} capabilities,
in this way the behaviour can be moved (at runtime) from a host to another one that implements the same capabilities.
%
The association between a component and a single capability do not necessarily imply that the component can be executed only on a single host,
but it is the way to specify the minimum requirements for the host that will execute the component.

\lstinputlisting[
    float=ht,
    language=Kotlin,
    caption={
        Example of the usage of the domain-specific language for the system configuration.
        The example configures two types of devices, and for each device defines the components that compose it and which capabilities requires for the execution.
    },
    label=lst:system-configuration,
]{listings/SystemConfig.kt}

>>>>

\subsection{Infrastructure and requirements}

The infrastructure \ac{dsl} captures the concepts of
\emph{device type}, \emph{component}, \emph{capability}, and \emph{requirement}.
%
A reference sample is presented in \Cref{lst:system-configuration}.
%
The DSL provides simple means to define capabilities as types in the host language,
and then to associate them to pulverised components for each device type.
%
This \ac{dsl} is meant to define constraints that the application imposes on the infrastructure,
ruling out configurations that are not capable to support the system
(for instance, deploying the sensor component of a device in a host that exposes no sensor).
%
All combinations of components and capabilities that are defined as supported become instead amenable to
\emph{runtime reconfiguration}.
%
Notice, for instance, that \texttt{Behavior} in \texttt{iot-sensor} is defined as executable on any of host exposing
\texttt{HighCPU} and/or \texttt{EmbeddedDevice} as capabilities:
it implies that the component can be moved from at runtime across any host implementing any such capability.

\lstinputlisting[
    float=ht,
    language=Kotlin,
    caption={
        Example infrastructure configuration,
        defining three capabilities and a system composed of two device types,
        each component of which is then bound to the set of capabilities it needs to execute.
    },
    label=lst:system-configuration,
]{listings/SystemConfig.kt}

\subsection{Runtime and reconfiguration}
